\documentclass[7pt]{article}
\usepackage[T1]{fontenc}
\usepackage{physics}
\usepackage{amssymb}
\newlength{\rulethickness}
\setlength{\rulethickness}{1.2pt}
\newlength{\rulelength}
\setlength{\rulelength}{15cm}
\usepackage[left=2cm, right=2cm, top=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{amsmath,amsthm,amscd}
\usepackage[colorlinks]{hyperref}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{xparse}
\usepackage{soul}


\begin{document}

Multiple regression is applicable to analyzing relatively small and well-organized datasets. For extracting information from considerably larger datasets such as Big Data, typically more specific tools are required; regardless of if they are obtained from traditional data sources or from the more non-traditional sources where datasets are typically not labelled. Machine learning in itself is wholly distinct from the field of statistics although it does build upon much of the same principles. 

Machine learning, the ensembole of techniques lies with the broader field of artificial intelligence and allow for intelligent decision making. Note that the main goal in a statistical regression ultimately is to reduce  residuals error and formalize relationships within a dataset by fitting a linear model to our dataset. Now although machine learning might borrow many of the same models as that of statistics, the ensemble of approaches is directed to solve a particular problem by (1) learning from the data, (2) through learning off an experience and (3) to therefore achieve some predetermined level of performance.

We may adopt supervised learning or unsupervised learning; with unsupervised learning our dataset is both unlabelled and there is no inherent target in the data. In supervised learning our dataset has both a target and the data itself will always be labelled. We may further define supervised learning 1) as designed to classify data (for example CART, random forests and neural networks) or 2) designed to learn the data (for example linear models or non-linear models).  With unsupervised learning our dataset is both unlabelled and there is no defined target. Unsupervised learning by contrast is typically used to cluster data. Additionally a third qualification of data would be reinforcement learning, where the data essentially learns from itself.

\subsection{Generalized Linear Models}

We may generalize a standard regression framework as being consistenet with the Generalized Linear Model (GLM); where we assume that the target variable ($Y$) is normally distributed, errors are normally distributed ($\varepsilon_i$), the features $X$ are fixed and the variance $\varepsilon_i$ is constant. 
 \end{document} 